Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-05-28 reviewer_response.txt

>Moreover, the authors need to add the statistical significance of the
results in tables 2 and 3 as the approaches often differ only in the second
decimal place.

We have added statistical significance information.

>In Table 2, it would be helpful to have also the results for
only the cover function (Lattice-cl-ovr), to determine how much the other
functions contribute.

Thank you for the suggestion. This has been added to the revised version.

@@

> The paper also needs to add a list of existing MWE lexica or lexical
resources with MWEs available to the community (e.g. those listed in the MWE
community website, or available in WordNet or other resources).

We have to demurr on this. Our paper is not about MWEs specifically, we do not use MWE resources to build our model nor to evaluate it, so a focus on available MWE resources seems a significant detour, especially given the space constraints.  It would also be very difficult to do the topic justice, especially given our cross-linguistic interest.

>Stylistically the text would also benefit from a revision that splits
sentences that are too long (there are several throughout the text). For
instance, the last sentence in the first paragraph of the introduction is 9
lines long: 'We present an effective, expand- able, and above all tractable
new approach to com- prehensive multiword lexicon acquisition that aims to
find a middle ground between standard MWE ac- quisition approaches based on
association measures (Ramisch, 2014), and more sophisticated statistical
models (Newman et al., 2012) which fail to scale to the large corpora which
are the main sources of the distributional information in modern NLP
systems.').

Thank you for your suggestion. We have split up some of the longer sentences, hopefully improving the readability.

@@

> Moreover, some passages are copied from Brooke et al. (2015), but lack the
citation, such as:
     *"Other mea- sures specifically designed to address sequences of larger
than two words include: the c-value (Frantzi et al., 2000), a metric
designed for term extraction which weights term frequency by the log length
of the n-gram while penalizing n-grams that appear in frequent larger ones;
and mutual expectation (Dias et al., 1999), which produces a normalized
statistic that reflects how much a candidate phrase resists the omission of
any particular word." (page 2) and
     *"include that of Newman et al. (2012), who used a generative Dirichlet
Process model which jointly creates a linear segmentation of the corpus and
a multiword vocabulary" (page 3)
There are also other instances, and these need to be rephrased.

We have rephrased the relevant parts of the literature review, though the basic content is unchanged.

> For the annotations, the text mentions 3 annotators, but doesn't specify
whether they were different for each of the 3 languages.

Yes, they were different for each of the 3 languages. Since they were native (first language) speakers of each of the relevant languages, we believe this implies that they were different across languages.

@@

Reviewer C:

> Where I had trouble was with the details of the model. First of all, much ofit seemed to be ad hoc; even accepting the notion of LPR from prior work,
there are many heuristic (or at least not obviously natural) choices made to
operationalize the general lattice idea mathematically. Second, even if the
model is reasonable, it is not entirely clear how the different parts fit
together into an optimization problem. There is mention of a parameter C;
and there is a notion of nodes being activated or not (I don’t think
notation is introduced for these binary variables, though it would be
appropriate). Are these the only things that have to be tuned? Is the
calculation of explainedness deterministic based on these? There is a greedy
search to optimize explainedness of the nodes in the lattice, subject to
various heuristics. Presenting a formal algorithm for the optimization may
clarify things considerably.

We have reorganized the method section and added an explicit objective function, which should help with some of the problems you identified. In terms of the central optimization problem, the only variables are exactly the on/off status of each node, and, if we exclude the parameters used in the creation of the lattice (e.g. the n-gram frequency threshold) and those involved in the efficiency restrictions, the only (hyper)parameter in the optimization is C; we have a included psuedocode for optimization algorithm. With regards to the ad hoc parts of the model, we have added a discussion separating the core aspects of the model from some of the more ad hoc choices made in the particular instantions of component functions (such as clearing), making it clear that we believe these can potentially be improved on (both in terms of performance as well as mathematical elegance), and that our primary purpose here is to show that overall architecture of the model is a promising one.

### 2017-05-29 tacl.tex
fixed inconsistent notation

We include gapped or non-contiguous $n$-grams in our analysis, in acknowledgment of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English \cite{Dehe:2002}, and noun--verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}. Having said this, there are generally strong syntactic and length \cite{Wasow:2002} restrictions on what can constitute a gap, which we capture in the form of a language-specific POS-based regular expression (see \secref{sec:evaluation} for details).
This greatly lowers the number of potentially gapped $n$-gram types, increasing precision and efficiency for negligible loss of recall. We also exclude punctuation and lemmatize the corpus, and enforce an $n$-gram count threshold. As long as the count threshold  is substantially above 1, efficient extraction of all $n$-grams can be done iteratively: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then pairs of instances of these $i$-grams with $(i-1)$ words of overlap are found, which derives a set of $(i+1)$-grams which necessarily includes all those over the frequency threshold.

Once a set of relevant $n$-grams is identified and counted, other statistics required to calculate the \termdef{Lexical Predictability Ratio} (``LPR'') for each word in the $n$-gram are collected. LPR is a measure of how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words). Formally, the LPR for word $w_i$ in the context of a word sequence $w_1,..., w_i, ..., w_{n}$ with POS tag sequence $t_1, ..., t_{n}$, is given by:
\begin{displaymath}
\LPR(w_i,w_{1,n}) = \max_{1 \leq j < k \leq n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
\end{displaymath}
where $w_{j,k}$ denotes the word sequence $w_j,..., w_{i-1}, w_{i+1}, ..., w_{k}$ excluding $w_{i}$ (similarly for $t_{j,k}$). Note that the lower bound of LPR is 1, since the ratio for a word with no context is trivially 1. We use the same equation for gapped $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics. Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase, resulting in the minimum LPR of 1 even for entirely formulaic sequences, an undesirable result.

@@

\termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice. For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of\ex{keep \gap under wraps}, with the idea that these occurrences have already been explained by the longer $n$-gram. If enough subsuming $n$-grams are on, then the shorter $n$-gram will be discounted to the extent that it will be turned off, preventing redundancy. This effect is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $s_1\dotts s_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes). Then, the $\cover(t)$ score for a covered node $t$ is:
\begin{displaymath}
\cover(t) = \max\Big(0,\frac{c(t) - \sum_{i=1}^{m}{c(s_i)}}{c(t)}\Big)
\end{displaymath}
This is intended as a simple, quick-to-calculate approximation of the result of recalculating minLPR with the counts corresponding to the covering nodes actually removed. \cover takes on values in the range 0 to 1, with 1 being the default when no covering is occurring.

@@

In general, covering prefers turning on longer, covering $n$-grams since doing so explains nodes lower in the lattice. Not surprisingly, it is generally desirable to have a mechanism working in opposition, \ie one which views shorter FS as helping to explain the presence of longer $n$-grams which contain them, beyond the FS-neutral syntactic explanation provided by minLPR. \termdef{Clearing} does this by changing the increasing the explainedness of nodes higher in the lattice when a lower node is turned-on. The basic mechanism is similar to covering, except that counts cannot be made use of in the same way---whereas it makes sense to explain covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams are from the covering $n$-gram), in the reverse direction this logic fails.

A simple but effective solution which avoids introducing extra hyperparameters is to make use of the minLPR values of the relevant nodes. In the most common two-node situation, we increase the explainedness of the cleared node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher. Generalized to the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
%in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
\begin{displaymath}
\clear(t) = \prod_{i=1}^{m}{\min\Big(1,\frac{\minLPR(t)}{\minLPR(u_i)}\Big)}
\end{displaymath}
where $u_i$ is the $i$th clearing node of $t$, \ie turned-on nodes below $t$ in the lattice. We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS. For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(t)$ will be 0.5. Like \cover, \clear takes on values in the range 0 to 1, with 1 being the default when no clearing occurs. Note that one major advantage with this particular formulation of clearing is that low-LPR nodes will be unable to clear higher LPR nodes above them in the lattice; otherwise, bad FS like \ex{of the} might be selected as FS based purely to increase the explainedness of the many $n$-grams they appear in.

@@

In order to capture the current state of the model and provide an overall explainedness score, we introduce two indicator functions: $I_{on}(t)$ is 1 if $t$ is on and 0 if $t$ is off ; $I_{\mathit{off}}(t)$ is the reverse. The objective function maximized by the model is then the explainedness ($expl$) across all the nodes of the lattice, which can be defined in terms of minLPR and the node interaction functions:

\begin{multline}
expl(t_1,...,t_N) = \prod_{i=1}^{N}{I_{on}(t_i)  C^{-\overlap(t_1)}} \\ + I_{\mathit{off}}(t_i) minLPR(t_i)^{-\cover(t_i) \cdot \clear(t_i)}
\end{multline}
\noindent
When a node is off, its explainedness is the inverse of its minLPR, except if there are covering or clearing nodes which explain it by pushing the exponent of minLPR towards zero. When the node is on, its explainedness is the inverse of a fixed cost hyperparameter C, though this cost is increased if it overlaps with other active nodes. 
All else being equal, when $\minLPR(t) > C$, a node will be selected as an FS, and so, independent of the node interactions, C can be viewed as the threshold for the minLPR association measure under a traditional approach to MWE identification. There is no upper bound on $C$, but empirically, we have found values in the range $[3,6]$ give reasonable results for the languages presented in this paper.

@@

\begin{algorithm}
	\caption{Optimization algorithm. $N$ is an ordered list of the nodes in the lattice. Nodes (designated by $n$) contain pointers to the nodes immediately linked to them in the lattice. States (designated by $s$) indicate whether each node is $ON$ or $OFF$. Explainedness values are indicated by $e$.}
	\label{alg:opt}
	\begin{algorithmic}

	\Function{LocalOpt}{$s_{start}, n, N_{rev}, N_{af\hspace{-0.1em}f}$}
		\State $s_{start} \gets \Call{Set}{s, n, ON}$
		\State $Q \gets \Call{EmptyQueue}{\null}$
		\State $e_{best} \gets 0$
		\State $s_{best} \gets NULL$
		\State \Call{Push}{Q,$s_{start}$}
		\Repeat
			\State $s_{curr} \gets \Call{Pop}{Q}$
			\State $e_{curr} \gets \Call{CalcExpl}{s_{curr}, N_{af\hspace{-0.1em}f}}$
			\For{$n_{rev} \textrm{ in } N_{rev}$}
					\State $s_{new} \gets \Call{Set}{s_{curr},n_{rev}, OFF}$
					\State $e_{new} \gets\Call{CalcExpl}{s_{new}, N_{af\hspace{-0.1em}f}}$
					\If{$ e_{new} > e_{curr}$}

					\State \Call{Push}{$Q, s_{new}$}
					\If{$e_{new} > e_{best}}$:
							\State $e_{best} \gets e_{new}$
							\State $s_{best} \gets s_{new}$
					\EndIf
					\EndIf
				\EndFor
		\Until{\Call{IsEmpty}{Q}}
	\State \Return $s_{best}$
	\EndFunction
\State
\State \Call{FrequencySortReverse}{$N$}
\State $s \gets \Call{InitializeAllOff}{N}$
\Repeat
	\State $Changed \gets FALSE$
		\For{$n \textrm{ in } N$}
		\State $N_{rev} \gets \Call{GetRelevant}{n,N}$
		\State $N_{af\hspace{-0.1em}f} \gets \Call{GetAffected}{N_{rev},N}$
		\State $s_{new} \gets \Call{LocalOpt}{s,n,N_{rev},N_{af\hspace{-0.1em}f}}$
		\If{$s_{new} \neq s$}
			\State $s \gets s_{new}$
			\State $Changed \gets TRUE$
		\EndIf
		\EndFor
\Until{$!Changed$}

\end{algorithmic}

\end{algorithm}

@@

We created small development sets for each corpus and used them to do a thorough testing of parameter settings. Although it is generally possible to increase precision by increasing $C$, we found that across corpora we were always obtained near-optimal results using a $C$ of 4, so to demonstrate the usefulness of the lattice technique as an entirely off-the-shelf tool, we present the results using identical settings for all four corpora. We treat covering as a fundamental part of the Lattice model, but to investigate the efficacy of other node interactions within the model we present results with each of overlap and clearing node interactions turned off.

@@

 \begin{center}
 \begin{tabular}{lccccccc}
\hline
& & & & \multicolumn{4}{c}{\bf{By Length (\%) }} \\
       \cmidrule(lr){5-8}	
\bf{Lexicon} & \bf{Size} & \bf{POS types} & \bf{Gapped} (\%) & \bf{2} & \bf{3} & \bf{4}  & \bf{5+} \\ 
\hline
English ICWSM & 202k & 16.8k & 18.3 & 46.7 & 30.1 & 15.0 & 7.5  \\
English BNC & 374k &  30.0k& 26.1& 38.8 & 36.6 & 18.1 & 7.7 \\
Croatian & 172k & 6.7k & 7.9& 55.0& 31.4 & 10.3 & 3.2 \\
Japanese & 218k &  29.4k &7.9& 39.5 & 31.1& 16.8 & 12.6 \\
\hline
\end{tabular}
  \caption{Statistics for the lexicons created by our lattice method}
	 \label{tab:lexstats}

@@

What is perhaps most striking is the non-English examples is how poorly some FS translate: many good FS in these languages become extremely awkward when translated into English. This is expected of course for idioms like \ex{biti general poslije bitke} (be the general after the battle, \ie hindsight is 20/20), but it extends to other relatively compositional  constructions like \begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} (repeat occurrences of \gap like this) and \ex{前期\ 比} (first half comparison). This highlights the importance of focusing on FS when learning a language, since many FS do not translate well (though some short ones do, particularly for languages in the same family). Though some of the errors seem to be the result of extra material added to an good FS, for instance \ex{promet teretnih vozila} (good vehicle traffic), most, again, are somewhat inexplicable artifacts of the corpus they were built from collected, like \ex{austrijski investitor} (Austrian investor).

@@

In \secref{sec:background}, we noted than FS is generally a much broader category than MWE, which we take as referring to terms which carry significant non-compositional meaning. We decided to investigate the distinction at a practical level by annotating the positive examples in the ICWSM test set for being MWE or non-MWE FS.\footnote{The set was exhaustively annotated by two annotators ($\kappa$: 0.73), and then conflicts were resolved through discussion.}. First, we note that only 0.28 of our FS types were labeled MWE; this is in contrast to, for instance, the annotation of \newcite{Schneider14a} where ``weak'' MWE make up a small fraction of MWE types. Even without any explicit representation of compositionality, our model did much better identifying MWE FS than non-MWE FS: recall for the former was 0.71, whereas recall for the latter was just 0.34. This may simply reflect, however, the fact that a disproportionate number of MWE were noun-noun compounds, which are fairly easy for the model to identify.

Due to the lack of spaces between words and an agglutinative morphology, the standard approach to tokenization and lemmatization in Japanese involves morphological rather than word segmentation. In terms of the content of the resulting lexicon we believe the effect of this difference is modest, since much of the extra FS in Japanese would simply be individual words in other languages (which could be viewed as being trivially part of the FS lexicon). However, from a theoretical perspective we might very much prefer to build FS for all languages starting from morphemes rather than words. Such a framework could, for instance, capture inflectional flexibilty versus fixedness directly in the model, with fixed inflectional morphemes included as an distinct element of the FS and flexible morphemes becoming gaps. However, for many languages this would result in a huge blow up in complexity with only modest increases in the scope of FS identification. Though it is indisputable that inflectional fixedness is part of the lexical information contained in an FS, in practice this sort of information can be efficiently derived post hoc using corpus statistics.

@@

Though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, F-scores become unreliable when there are very few positive examples, such as with most of our gapped $n$-gram test sets. To do a reliable, focused evaluation of FS with gaps, we would need many more examples than can be produced with straightforward sampling. One option we might consider is adding additional filtering to the sampling processes, for instance using the LPR metric to exclude large numbers of unpromising $n$-grams.

>>>>

We include gapped or non-contiguous $n$-grams in our analysis, in acknowledgment of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English \cite{Dehe:2002}, and noun-verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}. Having said this, there are generally strong syntactic and length restrictions on what can constitute a gap \cite{Wasow:2002}, which we capture in the form of a language-specific POS-based regular expression (see \secref{sec:evaluation} for details).
This greatly lowers the number of potentially gapped $n$-gram types, increasing precision and efficiency for negligible loss of recall. We also exclude punctuation and lemmatize the corpus, and enforce an $n$-gram count threshold. As long as the count threshold  is substantially above 1, efficient extraction of all $n$-grams can be done iteratively: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then pairs of instances of these $i$-grams with $(i-1)$ words of overlap are found, which derives a set of $(i+1)$-grams which necessarily includes all those over the frequency threshold.

Once a set of relevant $n$-grams is identified and counted, other statistics required to calculate the \termdef{Lexical Predictability Ratio} (``LPR'') for each word in the $n$-gram are collected. LPR is a measure of how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words). Formally, the LPR for word $w_i$ in the context of a word sequence $w_1,..., w_i, ..., w_{n}$ with POS tag sequence $t_1, ..., t_{n}$ is given by:
\begin{displaymath}
\LPR(w_i,w_{1,n}) = \max_{1 \leq j < k \leq n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
\end{displaymath}
where $w_{j,k}$ denotes the word sequence $w_j,..., w_{i-1}, w_{i+1}, ..., w_{k}$ excluding $w_{i}$ (similarly for $t_{j,k}$). Note that the lower bound of LPR is 1, since the ratio for a word with no context is trivially 1. We use the same equation for gapped $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics. Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase, resulting in the minimum LPR of 1 even for entirely formulaic sequences---an undesirable result.

@@

\termdef{Soft covering} is used in cases when a single $n$-gram does not entirely account for another, but a turned-on $n$-gram to some extent may explain some of the statistical irregularity of one lower in the lattice. For instance, in \figref{fig:example} \ex{keep \gap under} is not hard-covered by \ex{keep \gap under wraps} (since there are FS such as \ex{keep \gap under surveillance}, \ex{keep it under your hat}, \etc), but if \ex{keep \gap under wraps} is tagged as an FS, we nevertheless want to discount the portion of the \ex{keep \gap under} counts that correspond to occurrences of \ex{keep \gap under wraps}, with the idea that these occurrences have already been explained by the longer $n$-gram. If enough subsuming $n$-grams are on, then the shorter $n$-gram will be discounted to the extent that it will be turned off, preventing redundancy. This effect is accomplished by increasing the turned-off explainedness of \ex{keep \gap under} (and thus making turning on less desirable) in the following manner: let $c(\cdot)$ be the count function, and $a_1,\dotts, a_m$ be any turned-on nodes which are above $t$ in the lattice (covering nodes). Then, the $\cover(t)$ score for a covered node $t$ is:
\begin{displaymath}
\cover(t) = \max\Big(0,\frac{c(t) - \sum_{i=1}^{m}{c(a_i)}}{c(t)}\Big)
\end{displaymath}
This is intended as a simple, quick-to-calculate approximation of the result of recalculating minLPR with the counts corresponding to the covering nodes actually removed. The \cover score takes on values in the range 0 to 1, with 1 being the default when no covering is occurring.

@@

In general, covering prefers turning on longer, covering $n$-grams since doing so explains nodes lower in the lattice. Not surprisingly, it is generally desirable to have a mechanism working in opposition, \ie one which views shorter FS as helping to explain the presence of longer $n$-grams which contain them, beyond the FS-neutral syntactic explanation provided by minLPR. \termdef{Clearing} does this by increasing the explainedness of nodes higher in the lattice when a lower node is turned-on. The basic mechanism is similar to covering, except that counts cannot be made use of in the same way---whereas it makes sense to explain covered nodes in proportion to the counts of their covering nodes (since the counts of the covered $n$-grams are from the covering $n$-gram), in the reverse direction this logic fails.

A simple but effective solution which avoids introducing extra hyperparameters is to make use of the minLPR values of the relevant nodes. In the most common two-node situation, we increase the explainedness of the cleared node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher. Generalized to the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
%in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
\begin{displaymath}
\clear(t) = \prod_{i=1}^{m}{\min\Big(1,\frac{\minLPR(t)}{\minLPR(b_i)}\Big)}
\end{displaymath}
where $b_i$ is the $i$th clearing node of $t$, \ie turned-on nodes below $t$ in the lattice. We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS. For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(t)$ will be 0.5. Like \cover, \clear takes on values in the range 0 to 1, with 1 being the default when no clearing occurs. Note that one major advantage with this particular formulation of clearing is that low-LPR nodes will be unable to clear higher LPR nodes above them in the lattice; otherwise, bad FS like \ex{of the} might be selected as FS based purely to increase the explainedness of the many $n$-grams they appear in.

@@

In order to capture the current state of the model and provide an overall explainedness score, we introduce two indicator functions: $I_{\mathit{on}}(t)$ is 1 if $t$ is on and 0 if $t$ is off ; $I_{\mathit{off}}(t)$ is the reverse. The objective function maximized by the model is then the explainedness ($\mathit{expl}$) across all the nodes of the lattice, $t_1,\dots,t_{|T|} \in T$, which can be defined in terms of minLPR and the node interaction functions:
%
\begin{multline}
	\mathit{expl}(T) = \prod_{i=1}^{|T|}{I_{\mathit{on}}(t_i)\cdot C^{-\overlap(t_1)}} \\ + I_{\mathit{off}}(t_i)\cdot\minLPR(t_i)^{-\cover(t_i) \cdot \clear(t_i)}
\end{multline}
\noindent
When a node is off, its explainedness is the inverse of its minLPR, except if there are covering or clearing nodes which explain it by pushing the exponent of minLPR towards zero. When the node is on, its explainedness is the inverse of a fixed cost hyperparameter $C$, though this cost is increased if it overlaps with other active nodes. 
All else being equal, when $\minLPR(t) > C$, a node will be selected as an FS, and so, independent of the node interactions, $C$ can be viewed as the threshold for the minLPR association measure under a traditional approach to MWE identification. There is no upper bound on $C$, but empirically, we have found values in the range $[3,6]$ give reasonable results for the languages presented in this paper.

@@

\begin{algorithm}
	\caption{Optimization algorithm. $T$ is an ordered list of the nodes in the lattice. Nodes (designated by $t$) contain pointers to the nodes immediately linked to them in the lattice. States (designated by $s$) indicate whether each node is $\mathrm{ON}$ or $\mathrm{OFF}$. Explainedness values are indicated by $e$.}
	\label{alg:opt}
	\begin{algorithmic}

	\Function{LocalOpt}{$s_{\mathit{start}}, t, T_{\mathit{rev}}, T_{\mathit{aff}}$}
		\State $s_{\mathit{start}} \gets \Call{Set}{s, t, \mathrm{ON}}$
		\State $Q \gets \Call{EmptyQueue}{\null}$
		\State $e_{\mathit{best}} \gets 0$
		\State $s_{\mathit{best}} \gets \mathrm{NULL}$
		\State $\Call{Push}{Q, s_{\mathit{start}}}$
		\Repeat
			\State $s_{\mathit{curr}} \gets \Call{Pop}{Q}$
			\State $e_{\mathit{curr}} \gets \Call{CalcExpl}{s_{\mathit{curr}}, T_{\mathit{aff}}}$
			\For{$t_{\mathit{rev}} \textrm{ in } T_{\mathit{rev}}$}
					\State $s_{\mathit{new}} \gets \Call{Set}{s_{\mathit{curr}},t_{\mathit{rev}}, \mathrm{OFF}}$
					\State $e_{\mathit{new}} \gets\Call{CalcExpl}{s_{\mathit{new}}, T_{\mathit{aff}}}$
					\If{$ e_{\mathit{new}} > e_{\mathit{curr}}$}

					\State $\Call{Push}{Q, s_{\mathit{new}}}$
					\If{$e_{\mathit{new}} > e_{\mathit{best}}}$:
						\State $e_{\mathit{best}} \gets e_{\mathit{new}}$
							\State $s_{\mathit{best}} \gets s_{\mathit{new}}$
					\EndIf
					\EndIf
				\EndFor
		\Until{$\Call{IsEmpty}{Q}$}
	\State \Return $s_{\mathit{best}}$
	\EndFunction
\State
\State $\Call{FrequencySortReverse}{T}$
\State $s \gets \Call{InitializeAllOff}{T}$
\Repeat
	\State $\mathit{Changed} \gets \mathrm{FALSE}$
		\For{$t \textrm{ in } T$}
		\State $T_{\mathit{rev}} \gets \Call{GetRelevant}{t,T}$
		\State $T_{\mathit{aff}} \gets \Call{GetAffected}{T_{\mathit{rev}},T}$
		\State $s_{\mathit{new}} \gets \Call{LocalOpt}{s,t,T_{\mathit{rev}},T_{\mathit{aff}}}$
		\If{$s_{\mathit{new}} \neq s$}
			\State $s \gets s_{\mathit{new}}$
			\State $\mathit{Changed} \gets \mathrm{TRUE}$
		\EndIf
		\EndFor
\Until{$!\mathit{Changed}$}
\end{algorithmic}
\end{algorithm}

@@

We created small development sets for each corpus and used them to do a thorough testing of parameter settings. Although it is generally possible to increase precision by increasing $C$, we found that across corpora we always obtained near-optimal results using a $C$ of 4, so to demonstrate the usefulness of the lattice technique as an entirely off-the-shelf tool, we present the results using identical settings for all four corpora. We treat covering as a fundamental part of the Lattice model, but to investigate the efficacy of other node interactions within the model we present results with each of overlap and clearing node interactions turned off.

@@

 \begin{center}
 \begin{tabular}{lccccccc}
\toprule
& & & & \multicolumn{4}{c}{\bf{By Length (\%) }} \\
       \cmidrule(lr){5-8}	
\bf{Lexicon} & \bf{Word types} & \bf{POS types} & \bf{Gapped} (\%) & 2 & 3 & 4 & 5+ \\ 
\midrule
English ICWSM & 202k & 16.8k & 18.3 & 46.7 & 30.1 & 15.0 & 7.5  \\
English BNC & 374k &  30.0k& 26.1& 38.8 & 36.6 & 18.1 & 7.7 \\
Croatian & 172k & 6.7k & 7.9& 55.0& 31.4 & 10.3 & 3.2 \\
Japanese & 218k &  29.4k &7.9& 39.5 & 31.1& 16.8 & 12.6 \\
\bottomrule
\end{tabular}
  \caption{Statistics for the lexicons created by our lattice method}
	 \label{tab:lexstats}

@@

What is perhaps most striking about the non-English examples is how poorly some FS translate: many good FS in these languages become extremely awkward when translated into English. This is expected of course for idioms like \ex{biti general poslije bitke} (be the general after the battle, \ie hindsight is 20/20), but it extends to other relatively compositional  constructions like 
\begin{CJK*}{UTF8}{min} \ex{こう\ 言う\ \gap\ が\ 続く} \end{CJK*} 
(repeat occurrences of \gap like this) and 
\begin{CJK*}{UTF8}{min} \ex{前期\ 比} \end{CJK*} 
(first half comparison). This highlights the importance of focusing on FS when learning a language, since many FS do not translate well (though some short ones do, particularly for languages in the same family). Though some of the errors seem to be the result of extra material added to an good FS, for instance \ex{promet teretnih vozila} (good vehicle traffic), most, again, are somewhat inexplicable artifacts of the corpus they were built from collected, like \ex{austrijski investitor} (Austrian investor).

@@

In \secref{sec:background}, we noted than FS is generally a much broader category than MWE, which we take as referring to terms which carry significant non-compositional meaning. We decided to investigate the distinction at a practical level by annotating the positive examples in the ICWSM test set for being MWE or non-MWE FS.\footnote{The set was exhaustively annotated by two annotators ($\kappa$: 0.73), and then conflicts were resolved through discussion.} First, we note that only 0.28 of our FS types were labeled MWE; this is in contrast to, for instance, the annotation of \newcite{Schneider14a} where ``weak'' MWE make up a small fraction of MWE types. Even without any explicit representation of compositionality, our model did much better identifying MWE FS than non-MWE FS: recall for the former was 0.71, whereas recall for the latter was just 0.34. This may simply reflect, however, the fact that a disproportionate number of MWE were noun-noun compounds, which are fairly easy for the model to identify.

Due to the lack of spaces between words and an agglutinative morphology, the standard approach to tokenization and lemmatization in Japanese involves morphological rather than word segmentation. In terms of the content of the resulting lexicon we believe the effect of this difference is modest, since much of the extra FS in Japanese would simply be individual words in other languages (which could be viewed as being trivially part of the FS lexicon). However, from a theoretical perspective we might very much prefer to build FS for all languages starting from morphemes rather than words. Such a framework could, for instance, capture inflectional flexibilty versus fixedness directly in the model, with fixed inflectional morphemes included as a distinct element of the FS and flexible morphemes becoming gaps. However, for many languages this would result in a huge blow up in complexity with only modest increases in the scope of FS identification. Though it is indisputable that inflectional fixedness is part of the lexical information contained in an FS, in practice this sort of information can be efficiently derived post hoc using corpus statistics.

@@

%Though in general using the sampling methodology to build test sets has significant benefits in terms of providing a robust, replicable evaluation, F-scores become unreliable when there are very few positive examples, such as with most of our gapped $n$-gram test sets. To do a reliable, focused evaluation of FS with gaps, we would need many more examples than can be produced with straightforward sampling. One option we might consider is adding additional filtering to the sampling processes, for instance using the LPR metric to exclude large numbers of unpromising $n$-grams.
